Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-11 Moltres.tex
Some small fixes and add passage describing radial plot of fluxes.

\begin{align}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} &- \nabla \cdot D_g 
        \nabla \phi_g + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G 
        \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - 
        \beta) \nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
        \intertext{where}
        v_g &= \mbox{speed of neutrons in group g} \\ 
        \phi_g &= \mbox{flux of neutrons in group g} \\ 
        t &= \mbox{time} \\ 
        D_g &= \mbox{Diffusion coefficient for neutrons in group g} \\ 
        \Sigma_g^r &= \mbox{macroscopic cross-section for removal of neutrons 
        from group g} \\ 
        \Sigma_{g'\rightarrow g} &= \mbox{macroscopic cross-section of 
        scattering from g' to g} \\ 
        \chi_g^p &= \mbox{prompt fission spectrum, neutrons in group g} \\ 
        G &= \mbox{number of discrete groups, g} \\ 
        \nu &= \mbox{number of neutrons produced per fission} \\ 
        \Sigma_g^f &= \mbox{macroscopic cross section for fission due to neutrons in group g} \\ 
        \chi_g^d &= \mbox{delayed fission spectrum, neutrons in group g} \\ 
        I &= \mbox{number of delayed neutron precursor groups} \\ 
        \beta &= \mbox{delayed neutron fraction}\\
        \lambda_i &= \mbox{average decay constant of delayed neutron precursors 
        in precursor group i} \\ 
        C_i &= \mbox{concentration of delayed neutron precursors in precursor 
        group i} . 
\end{align}

@@

in the moderator.

and $Q_g$ is equal to $\gamma Q_f$, where $\gamma$ is a factor representing 
heat dissipation by gamma and neutron irradiation in the moderator.

Group constants are generated with either Serpent \cite{leppanen_serpent_2015} 
or Scale \cite{dehart_reactor_2011} by the modeler. Group constant temperature 
dependence is implmented via interpolation tables, which must be constructed 
separately for fuel and moderator regions.

@@

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group1.eps}
  \caption{Group 1 flux}
  \label{fig:group1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group2.eps}
  \caption{Group 2 flux}
  \label{fig:group2}
\end{figure}

The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
rises steadily with increasing z-coordinate. As one might expect, the temperature
gradient is negative in the radial direction.

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_temp.eps}
  \caption{Temperature}
  \label{fig:temp}
\end{figure}

\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
reactor. Not surprisingly, the channel concentrations are higher in fuel channels
with higher neutron fluxes and consequently a higher number of fission
events. Because of the small decay constant of the precursor, the maximum
concentration in any given channel occurs at the core outlet.

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre1.eps}
  \caption{Longest lived precursor concentration}
  \label{fig:pre1}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre6.eps}
  \caption{Shortest lived precursor concentration}
  \label{fig:pre6}
\end{figure}

>>>>

\begin{align}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} &- \nabla \cdot D_g
        \nabla \phi_g + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G
        \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 -
        \beta) \nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
        \intertext{where}
        v_g &= \mbox{speed of neutrons in group g} \\
        \phi_g &= \mbox{flux of neutrons in group g} \\
        t &= \mbox{time} \\
        D_g &= \mbox{Diffusion coefficient for neutrons in group g} \\
        \Sigma_g^r &= \mbox{macroscopic cross-section for removal of neutrons
        from group g} \\
        \Sigma_{g'\rightarrow g}^s &= \mbox{macroscopic cross-section of
        scattering from g' to g} \\
        \chi_g^p &= \mbox{prompt fission spectrum, neutrons in group g} \\
        G &= \mbox{number of discrete groups, g} \\
        \nu &= \mbox{number of neutrons produced per fission} \\
        \Sigma_g^f &= \mbox{macroscopic cross section for fission due to neutrons in group g} \\
        \chi_g^d &= \mbox{delayed fission spectrum, neutrons in group g} \\
        I &= \mbox{number of delayed neutron precursor groups} \\
        \beta &= \mbox{delayed neutron fraction}\\
        \lambda_i &= \mbox{average decay constant of delayed neutron precursors
        in precursor group i} \\
        C_i &= \mbox{concentration of delayed neutron precursors in precursor
        group i} .
\end{align}

@@

In this work $Q_g$ is set equal to $\gamma Q_f$, where $\gamma$ is a factor
representing heat dissipation by gamma and neutron irradiation in the moderator.

Group constants are generated by the modeler with either Serpent
\cite{leppanen_serpent_2015} or Scale \cite{dehart_reactor_2011}. Group constant
temperature dependence is implemented via interpolation tables, which must be
constructed separately for fuel and moderator regions.

@@

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group1.eps}
        \caption{The group 1 flux in this 2-D cylindrical axisymmetric model
        has the anticipated magnitude and canonical cosine shape ($r=0$ is center of core). }
  \label{fig:group1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group2.eps}
        \caption{The group 2 flux in this 2-D cylindrical axisymmetric model
        has the anticipated magnitude and canonical cosine shape ($r=0$ is center of core). }
  \label{fig:group2}
\end{figure}

\Cref{fig:flux_comparison} compares the fast and thermal neutron fluxes at the
reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
moderator regions and visa versa in fuel regions are even more apparent. The
larger fast flux magnitude is attributable to using \gls{BOL} fuel
composition. As the fuel salt reaches an equilibrium composition, the thermal
flux is expected to exceed that of the fast group.

\begin{figure}
  \centering
  \includegraphics{radial_group_comparison.eps}
  \caption{The thermal and fast flux profiles are compared at the core mid-plane
    ($z=H/2$) in this 2-D cylindrical axisymmetric model ($r=0$ is radial center
    of core). }
  \label{fig:flux_comparison}
\end{figure}

The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
rises steadily with increasing z-coordinate. As is expected, the temperature
gradient is negative in the radial direction.

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_temp.eps}
        \caption{The reactor core temperature peaks near the reactor outlet in
          this 2-D axisymmetric model because of fuel advection ($r=0$ is center
          of core).}
  \label{fig:temp}
\end{figure}

\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
reactor. Not surprisingly, the channel concentrations are higher in fuel channels
with higher neutron fluxes and consequently a higher number of fission
events. Because of the small decay constant of the precursor, the maximum
concentration in any given channel occurs at the core outlet due to advection.

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre1.eps}
        \caption{The concentration of the group of longest lived precursors
        ($\lambda = 1.24\cdot 10^{-2} s^{-1}$) peaks near the reactor outlet
        in this 2-D axisymmetric model ($r=0$ is center of core).}
  \label{fig:pre1}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre6.eps}
        \caption{The concentration of the group of shortest lived precursors
        ($\lambda = 3.07 s^{-1}$) peaks near the reactor center
        in this 2-D axisymmetric model ($r=0$ is center of core).}
  \label{fig:pre6}
\end{figure}
